Pillar 2 - Topic Modeling

### 2019-01-10 Pillar 2 - Topic Modeling.Rmd

>>>>

```{r visualization LDA, eval = F}
visualize_LDA(LDA_SCI_2 , id_plot = "SCI, k = 2" )
visualize_LDA(LDA_SCI_5 , id_plot = "SCI, k = 5" )
visualize_LDA(LDA_SCI_10, id_plot = "SCI, k = 10")

visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10", facet = T)
visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17", facet = T)
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25", facet = T)

visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))

visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
                              "Math", "Management and ?"))
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
              topic_names = c(
                "Information", "Psycho", "Bio", "Chem", "Sociology",
                "History", "skills", "Europe", "Philosophy", "IR",
                "Conference", "Law", "Media", "Philosophy", "Economics",
                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
```
